---
output: md_document
---

## Consuming tidiers

```{r 02-build-objects}
# build objects
library(redcapAPI)
rcon <- redcapConnection(url = "https://not-a-valid-url.org",
                         token = "Not-a-Valid-Token")
fit <- lm(mpg ~ qsec, data = mtcars)
```

Now suppose I wish to consume the `tidy.redcapApiConnection` method in another package.  This is accomplished easily enough by include `broom.extend` in the `Imports:` of the package `broom.consumeSpecific` and then calling the `tidy` method using the `broom.extend::tidy` syntax.  This is done in `broom.consumeSpecific`'s `consume` function.  

Note, we can confirm this works because `consume` reverts the tidy output from a tibble to a data frame.

```{r 02-demonstrate}
library(broom.consumeSpecific)
consume(rcon)
```

At this point, however, we are unable to run consume on objects that do not have `tidy` methods defined in `broom.extend`.  Since `broom.extend` only defines the tidier for `redcapApiConnection` objects, `consume` will fail when fun on `fit`

```{r 02-demonstrate2, error = TRUE}
consume(fit)
```