---
output: md_document
---

## Consuming with Arbitrary Tidiers

```{r 06-buld-objects}
# build objects
library(redcapAPI)
rcon <- redcapConnection(url = "https://not-a-valid-url.org",
                         token = "Not-a-Valid-Token")
fit <- lm(mpg ~ qsec, data = mtcars)
```

```{r 06-demonstrate, error = TRUE}
library(broom.consumeArbitrary)
consume(rcon)
consume(fit)

library(broom.extend)
consume(rcon)
consume(fit)

library(broom)
consume(fit)
```

There's a dirty, and likely inadvisable, hack behind this dark sorcery.  There is a `find_method` function in `broom.consumeArbitrary` that searches the packages on the search path for the tidier that applies to the object type.  The code for `find_method` is

```{r 06-find-method, eval = FALSE}
find_method <- function(generic = c("tidy", "glance", "augment"), class){
  generic <- match.arg(generic, c("tidy", "glance", "augment"))
  
  method_to_find <- paste0(generic, ".", class)
  
  pkg <- utils::find(generic)

  method <- 
    vapply(pkg, 
           function(x) any(method_to_find %in% 
                             utils::.S3methods(generic, 
                                               envir = getNamespace(sub("^.+[:]", "", x)))),
           logical(1))
  method <- method[method]
  
  package_namespace <- 
    search()[match(names(method), search())][1]
  
  package_namespace <- sub("^.+[:]", "", package_namespace)
  
  if (is.na(package_namespace)){
    stop("Could not find a `", generic, "` method for the `", class[1], "` class. ",
         "Either the package with the method is not loaded, or no such method has been written")
  }
  
  get(generic, envir = getNamespace(package_namespace))
}
```

It gets utilized in `consume` to define the `tidy` generic on the fly. In this manner, the `tidy` generic exists only within the context of `consume`.

```{r 06-consume, eval = FALSE}
consume <- function(x, ...){
  tidied <- find_method("tidy", class(x))(x, ...)

  as.data.frame(tidied)
}
```

The behaviors to note in this approach are

1. `consume` may be run on any arbitrary object with a `tidy` method defined on the search path.
2. The package containing the `tidy` method must be loaded using `library(package)`
3.  The order in which packages are loaded in unimportant.  We may load `broom.consumeArbitrary` before loading `broom`, and `consume` will work.
4.  `broom.consumeArbitrary` need not `Depends:` nor `Imports:` any package at all. But it will fail to execute without an appropriate tidier installed. Thus, it may be prudent to `Depends:` at least one package (most commonly, `broom`).